 

### 2023-03-11 thesis_final_version.Rmd
Revisions throughout and final version for External Reader

In Chapter 2, we focused on Madagascar—a low income country that is among the most vulnerable to the health consequences of climate change—and examine how health system visits for mental disorders may be shifting in response to climate change exposures such as changes in temperature, soil moisture, and the duration of tropical storms and cyclones. Drawing on meteorologic, geospatial, and health system data reported by 3,413 facilities in Madagascar from 2010 to 2020, we conducted an ecological analysis using negative binomial regression.  Our results indicated that warmer temperatures in the cooler central highlands were associated with a decrease in monthly reported visits for mental disorders, while higher soil moisture could lead to an increase in visits, particular in high flood-risk regions and after a three-month lag, indicating potential variation in the impact of climate change on mental health needs and system responses.

In Chapter 3, we investigated how Google search data for mental health symptoms might provide insight into the state of mental health during the COVID-19 pandemic. Using an interrupted time series approach with search data from U.S. counties, states, and international trends, we found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for searches related to anxiety and depression. These declines in searches, if taken as a reasonable proxy for population mental health, underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.

>>>>

In Chapter 2, we focused on Madagascar—a low income country that is among the most vulnerable to the health consequences of climate change—and examine how health system visits for mental disorders may be shifting in response to climate change exposures such as changes in temperature, soil moisture, and the duration of tropical storms and cyclones. Drawing on meteorologic, geospatial, and health system data reported by 3,413 facilities from 2010 to 2020, we conducted an ecological analysis using negative binomial regression.  Our results indicated that warmer temperatures in the cooler central highlands were associated with a decrease in monthly reported visits for mental disorders, while higher soil moisture could lead to an increase in visits, particular in high flood-risk regions and after a three-month lag, indicating potential variation in the impact of climate change on mental health needs and system responses.

In Chapter 3, I investigated how Google search data for mental health symptoms might provide insight into the state of mental health during the COVID-19 pandemic. Using an interrupted time series approach with search data from U.S. counties, states, and international trends, I found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for anxiety and depression. These declines in searches, if taken as a reasonable proxy for population mental health, underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.
